### 2013-11-24 phd/menger.tex
Minor tweaks to asrc implies 2-mark proof
housecleaning, added proximal game results

  \begin{proof}
    Let $\sigma(\mc{U}_0,0)$ cover $c(\mc{U}_0,0)$, and let $\sigma(\mc{U}_n,\mc{U}_{n+1},n+1)$ cover both $c(\mc{U}_{n+1},n+1)$ and $p(\mc{U}_n,\mc{U}_{n+1})$. If $\mc{U}_0,\mc{U}_1,\dots$ is any play by $C$, then for each $x\in X$, we note that one of the following must occur:
      \begin{itemize}
        \item $r_{\mc U_0}(x)=0$ and thus $x\in c(\mc U_0,0)\subseteq \bigcup \sigma(\mc{U}_0,0)$.
        \item $r_{\mc U_0}(x)=N+1$ for some $N\geq 0$ and:
        \begin{itemize}
          \item For all $n\leq N$, 
            \[
              n+1< r_{\mc U_{n+1}}(x)\leq N+1
            \] 
            and thus $x\in c(\mc U_{N+1},r_{\mc U_{n+1}}(x))=c(\mc U_{N+1},N+1)$.
          \item For some $n \leq N$,
            \[
              r_{\mc U_{n+1}}(x)< n+1 \leq r_{\mc U_n}(x)< N+1
            \]
            and thus $x\in c(\mc U_{n+1},r_{\mc U_{n+1}}(x))\subseteq c(\mc U_{n+1},n+1)$.
          \item For some $n \leq N$, 
            \[
              n+1 \leq r_{\mc U_n}(x)< N+1 < r_{\mc U_{n+1}}(x)
            \]
           and thus $x\in p(\mc U_n,\mc U_{n+1})$
         \end{itemize}
      \end{itemize}
  \end{proof}

@@

@@

  \begin{theorem}
    The following are equivalent for points-$G_\delta$ $X$:
      \begin{enumerate}[(a)]
        \item $S\win\rothgame{X}$
        \item $P\win\altrothgame{X}$
        \item $S\kmarkwin{k}\rothgame{X}$ for some $k\geq 1$
        \item $S\markwin\rothgame{X}$
        \item $P\prewin\altrothgame{X}$
        \item $X$ is almost countable
        \item $|X|\leq\omega$
      \end{enumerate}
  \end{theorem}

@@

  \begin{corollary}
    The following are equivalent for compact points-$G_\delta$ $X$:
      \begin{enumerate}[(a)]
        \item $S\win\rothgame{X}$
        \item $P\win\altrothgame{X}$
        \item $S\kmarkwin{k}\rothgame{X}$ for some $k\geq 1$
        \item $S\markwin\rothgame{X}$
        \item $P\prewin\altrothgame{X}$
        \item $X$ is almost countable
        \item $|X|\leq\omega$
        \item $C\not\win\rothgame{X}$
        \item $O\not\win\altrothgame{X}$
        \item $X$ is Rothberger
        \item $X$ is scattered
      \end{enumerate}
  \end{corollary}

>>>>

  \begin{proof}
    Let $\sigma(\mc{U}_0,0)$ cover $c(\mc{U}_0,0)$, and let $\sigma(\mc{U}_n,\mc{U}_{n+1},n+1)$ cover both $c(\mc{U}_{n+1},n+1)$ and $p(\mc{U}_n,\mc{U}_{n+1})$. If $\mc{U}_0,\mc{U}_1,\dots$ is any play by $C$, then for each $x\in X$, we note that one of the following must occur:
      \begin{itemize}
        \item $r_{\mc U_0}(x)=0$ and thus $x\in c(\mc U_0,0)\subseteq \bigcup \sigma(\mc{U}_0,0)$.
        \item $r_{\mc U_0}(x)=N+1$ for some $N\geq 0$ and:
        \begin{itemize}
          \item For all $n\leq N$, 
            \[
              r_{\mc U_{n+1}}(x)\leq N+1
            \] 
            and thus $x\in c(\mc U_{N+1},N+1)$.
          \item For some $n \leq N$, 
            \[
              r_{\mc U_n}(x)\leq N+1 < r_{\mc U_{n+1}}(x)
            \]
           and thus $x\in p(\mc U_n,\mc U_{n+1})$
         \end{itemize}
      \end{itemize}
  \end{proof}

@@

  \begin{definition}
    A space suggested by G: Give $\kappa^\sharp=(\kappa\times\oneptlind\kappa)\cup\{\infty\}$ the topology where $\{\alpha\}\times\kappa^\sharp$ is an open copy of $\oneptlind{\kappa}$, and neighborhoods of $\infty$ contain a set of the form $\kappa^\sharp\setminus(A\times\oneptlind\kappa)$ for some $A\in[\kappa]^\omega$.
  \end{definition}

  \begin{theorem}
    $F\kmarkwin{2}\mengame{\omega_1^\sharp}$
  \end{theorem}

  \begin{proof}
    Let $f_\alpha:\alpha\to\omega$ witness $S(\omega_1,\omega,\omega)$ for limit ordinals $\alpha<\omega_1$. Also note that there is a bijection $e:\omega_1\to[\omega_1]^{<\omega}$ such that $e\rest\alpha:\alpha\to[\alpha]^{<\omega}$ is also a bijection for each limit ordinal $\alpha<\omega_1$.

    We define the finite set $F(\alpha_n,\alpha_{n+1},n+1)$ to contain $e(\beta)$ for each $\beta<\alpha_n\cap\alpha_{n+1}$ such that either $f_{\alpha_{n+1}}(\beta)\leq n$ or $f_{\alpha_{n}}(\beta)\not=f_{\alpha_{n+1}}(\beta)$.

    If $\alpha_n<\omega_1$ for all $n<\omega$ with $\alpha=\min\{\alpha_{n+1}:n<\omega\}$ and $G\in[\alpha]^{<\omega}$, note that for each $\beta<\alpha$, either $f_{\alpha_n}(\beta)=N$ always, or $f_{\alpha_n}(\beta)\not=f_{\alpha_{n+1}}(\beta)$ for some $n$. Either way, $e(\beta)\subseteq F(\alpha_n,\alpha_{n+1},n+1)$ for some $n$, and thus every finite subset of $\alpha$ is contained in some $F(\alpha_n,\alpha_{n+1},n+1)$.

    If we let $R(\alpha)=\omega_1^\sharp\setminus(A\times\oneptlind\omega_1)$ and $U(\gamma,\alpha)=\{\gamma\}\times(\oneptlind\omega_1\setminus\alpha)$, then any open cover of $\omega_1^\sharp$ may be refined to be of the form $\mc U_\alpha = \{R(\alpha)\}\cup\{U(\gamma,\alpha):\gamma<\alpha\}\cup\{\{(\gamma,\beta)\}:\gamma,\beta<\alpha\}$ for some limit $\alpha$.

    Without loss of generality assume $\pl C$ plays only covers of the form $\mc U_\alpha$ for limit $\alpha$. Then we may define the $2$-Markov strategy $\sigma(\mc U_{\alpha_n},\mc U_{\alpha_{n+1}},n+1)$ to cover the sets:
      \[
        R(\alpha_{n+1})
      \]
      \[
        \bigcup \{U(\gamma,\alpha_{n+1}) : \gamma \in F(\alpha_n,\alpha_{n+1},n+1) \}
      \]
      \[
        \{(\gamma,\delta): \gamma,\delta\in F(\alpha_n,\alpha_{n+1},n+1)\}
      \]

    Let $\mc U_{\alpha_0},\mc U_{\alpha_1},\dots$ be an attack by $\pl C$, $\alpha=\min\{\alpha_{n+1}:n<\omega\}$ and $\alpha'=\sup\{\alpha_{n+1}:n<\omega\}$. Since $\infty\in R(\alpha_0)$ always, first consider $(\gamma,\infty)$ for $\gamma<\omega_1$. If $\gamma\geq\alpha_{n+1}$ for some $n$, then $(\gamma,\infty)\in R(\alpha_{n+1})$. Otherwise, $\gamma<\alpha$, but then $\gamma\in F(\alpha_n,\alpha_{n+1},n+1)$ for some $n$ and $(\gamma,\infty)\in U(\gamma,\alpha_{n+1})$.

    Lastly consider $(\gamma,\delta)$ for $\gamma,\delta<\omega_1$. If $\gamma\geq\alpha_{n+1}$ for some $n$, then $(\gamma,\delta)\in R(\alpha_{n+1})$.

    Otherwise, $\gamma<\alpha$. If $\delta\geq \alpha'$, then as $\gamma\in F(\alpha_n,\alpha_{n+1},n+1)$ for some $n$ we see $(\gamma,\delta)\in U(\gamma,\alpha_{n+1})$. If $\delta<\alpha$, then $\{\gamma,\delta\}\subseteq F(\alpha_n,\alpha_{n+1},n+1)$ for some $n$ and $(\gamma,\delta)$ is covered. The final case is when $\alpha\leq\delta<\alpha'$.

    (STILL MISSING STUFF)

    % If $\alpha_{n+1}=\beta$ is fixed for $n\in W\in[\omega]^\omega$, observe that $f_{\alpha_{n+1}}(\gamma)=f_\beta(\gamma)=N$ for all $n\in W$, and thus $\gamma\in F(\alpha_n,\alpha_{n+1},n+1)$ for some $n\in W\setminus N$. Thus $(\gamma,\delta)\in U(\gamma,\alpha)$ is covered.
  \end{proof}

  % \begin{lemma}
  %   For each infinite cardinal $\kappa$, the sentence $S(\kappa,\omega,\omega)$ implies there exists a function $F:[\kappa]^\omega\times[\kappa]^\omega\times\omega\to [\kappa]^{<\omega}$ such that for any choice of $A_n\in[\omega]^\omega$ and $G\in[\bigcap_{m<\omega}\bigcup_{m\leq n<\omega} A_{n+1}]^{<\omega}$, there exists an $n<\omega$ with $G\subseteq F(A_n,A_{n+1},n+1)$.
  % \end{lemma}

  % \begin{proof}
  %   Let $\Lim([\kappa]^\omega)\subseteq[\kappa]^\omega$ denote the countable subsets of $\kappa$ for which if a set contains $\alpha+n$, then it contains $\alpha+m$ for all $m<\omega$.

  %   Let $e:[\kappa]^{<\omega}\to\kappa$ be a bijection such that for every $A\in\Lim([\kappa]^\omega)$, $e\rest [A]^{<\omega}:[A]^{<\omega}\to A$ is a bijection.

  %   Then for $A,B\in\Lim([\kappa]^\omega)$ let $F(A,B,n+1)$ contain all $G\in[B]^{<\omega}$ satsifying $f_{B}(e(G))\leq n$, and also contain all $G\in[A\cap B]^{<\omega}$ satisfying $f_{A}(e(G))\not= f_{B}(e(G))$.

  %   Fix arbitrary $A_n\in[\omega]^\omega$ and $G\in[\bigcap_{m<\omega}\bigcup_{m\leq n<\omega} A_{n+1}]^{<\omega}$.
  % \end{proof}

  % \begin{theorem}
  %   $F\kmarkwin{2}\mengame{\omega_1^\sharp}$
  % \end{theorem}

  % \begin{proof}
  %   Let $f_A$ witness $S(\kappa,\omega,\omega)$ for each $A<[\kappa]^{\omega}$.

  %   Let $R(A)=\kappa^\sharp\setminus(A\times\oneptlind\kappa)$. Let $U(\gamma,A)=\{\gamma\}\times(\oneptlind{\kappa}\setminus A)$. Then note that every open cover has a pairwise disjoint open refinement of the form 
  %     \[
  %       \mc U_A = 
  %       \{R(A)\}\cup\{U(\gamma,A):\gamma\in A\}\cup\{\{(\gamma,\beta)\}:\gamma,\beta\in A\}
  %     \]
  %   Assume without loss of generality that all covers are of the form $\mc U_A$.

  %   % Rough idea: Let $\mc U_\alpha$ cover...

  %   % Let $\sigma(\mc U,\mc V,n+1)$ be a $2$-mark.

  %   % Let $F(\alpha_n,\alpha_{n+1},n+1) = \{\alpha<\alpha_n\cap\alpha_{n+1}:\sigma(\mc U_{\alpha_n},\mc U_{\alpha_{n+1}},n+1)$ covers $(\alpha,\beta)$ or $(\beta,\alpha)$ for some $\beta\}$.

  %   % Claim: It is not true that for all $\alpha,\beta<\alpha_0<\alpha_1<\dots$ there exists $n<\omega$ with $\alpha,\beta\in F(\alpha_n,\alpha_{n+1},n+1)$.

  %   % If so, then choose $\alpha,\beta<\alpha_0<\alpha_1<\dots$ such that $\alpha,\beta\not\in\bigcap_{n<\omega}F(\alpha_n,\alpha_{n+1},n+1)$. Then $\sigma$ covers neither $(\alpha,\beta)$ or $(\beta,\alpha)$ in response to the attack $\mc U_{\alpha_0},\mc U_{\alpha_1},\dots$
  % \end{proof}

  \centerline{Alster, Hurewicz}

  Besides various limited information characterizations of $\mengame{X}$, there are other interesting covering properties between $\sigma$-(relatively compact) and Menger.

  \begin{definition}
    A colleciton of subsets of a space $X$ is (\textbf{really}) \textbf{ample} if has a finite subcover for each (relatively) compact subset of $X$.
  \end{definition}

  \begin{proposition}
    Every ample cover of a regular space $X$ is really ample.
  \end{proposition}

  \begin{proof}
    Every relatively compact set $R$ is a subset of the compact set $\overline{R}$.
  \end{proof}

  \begin{definition}
    A space $X$ is (\textbf{relatively}) \textbf{Alster} if there exists a countable subcover for each (really) ample cover of $X$ by $G_\delta$ sets.
  \end{definition}

  \begin{proposition}
    Every regular relatively Alster space is Alster.
  \end{proposition}

  \begin{theorem}
    $X$ $\sigma$-compact $\Rightarrow$ $X$ Alster $\Rightarrow$ $X$ Menger
  \end{theorem}

  \begin{proof}
    Due to Leandro F. Aurichi and Franklin D. Tall in ``Lindel\"of spaces which are indestructible, productive, or D''.
  \end{proof}

  \begin{proposition}
    $X$ $\sigma$-(relatively compact) $\Rightarrow$ $X$ relatively Alster $\Rightarrow$ $X$ Menger
  \end{proposition}

  \begin{proof}
    If $X$ is $\sigma$-(relatively compact), then there exists a countable subcover for every really ample cover of $X$ by arbitrary sets.

    If $X$ is relatively Alster, we adapt Aurichi and Tall's argument for the previous theorem.

    Since relatively Alster implies Lindel\"of (all open covers of $X$ are relatively ample by definition of relatively compact), it is sufficient to consider open covers $\mc U_n = \{ U_n^m : m<\omega\}$ such that $U_n^m\subseteq U_n^{m+1}$. Then $\mc G=\{\bigcap_{n<\omega} U_n^{f(n)} : f\in \omega^\omega\}$ is a $G_\delta$ cover. To see that $\mc G$ is relatively ample, note for each relatively compact $K$ in $X$, $K$ is covered by something in each $\mc U_n$, and thus there is $f_K(n)\in\omega^\omega$ such that $K\subseteq \bigcap_{n<\omega} U_n^{f_K(n)}$.

    By relatively Alster, let $f_m\in\omega^\omega$ for $m<\omega$ so that $\mc G'=\{\bigcap_{n<\omega} U_n^{f_m(n)}:m<\omega\}$ covers $X$.

    Then let $\mc F_n = \{U_n^{f_m(n)}:m\leq n\}\in[\mc U_n]^{<\omega}$. Note that if $x\in X$, then $x\in \bigcap_{n<\omega} U_n^{f_{m_x}(n)}$ for some $m_x<\omega$ as $\mc G'$ is a cover. Thus $x\in U_{m_x}^{f_{m_x}(m_x)}$ and is covered by $\mc F_{m_x}$.
  \end{proof}

  \begin{example}
    Let the real numbers $R$ be given the topology generated by open intervals with countable sets removed. $R$ is not relatively Alster and $F\win\mengame{R}$. If $S(2^\omega,\omega,\omega)$ holds, then $F\kmarkwin{2}\mengame{R}$.
  \end{example}

  \begin{proof}
    Since points are $G_\delta$ and its relatively compact sets are all finite, a cover by singletons is really ample and has no countable subcover, showing $R$ is not relatively Alster.

    It was proven earlier that $F\win\mengame{R}$. Assuming $S(2^\omega,\omega,\omega)$, we construct a $2$-Mark\"ov strategy by first defining the following:
      \begin{itemize}
        \item Let $z_n$ enumerate the integers for $n<\omega$.
        \item For each open cover $\mc V$ of $R$, let $A(\mc V)$ be a countable set such that $[z_n,z_n+1)\setminus A(V)$ is $\mc V$-compact for each $n<\omega$.
        \item Let $f_A:A\to\omega$ for $A\subseteq R$ witness $S(2^\omega,\omega,\omega)$.
      \end{itemize}

    Then we may define $\sigma(\mc U_0,0)=\emptyset$ and define $\sigma(\mc U_n,\mc U_{n+1},n+1)$ such that it covers each of the following:
      \[
        \left(\bigcup_{m\leq n} [z_m,z_m+1)\right) \setminus A(\mc U_{n+1})
      \]
      \[
        \{f_{A(\mc U_{n+1})}^{-1}(m) : m\leq n\}
      \]
      \[
        \{x \in A(\mc U_n)\cap A(\mc U_{n+1}) : f_{A(\mc U_{n})}(x)\not= f_{A(\mc U_{n+1})}(x)\}
      \]

    For any attack $\mc U_0,\mc U_1,\dots$ on $\sigma$, let $x\in[z_n,z_n+1)$. 
      \begin{itemize}
        \item If $x\not\in A(\mc U_{n+1})$, then $x$ is covered in round $n+1$.
        \item If $x\in A(\mc U_{n+1})$, let $N=f_{A(\mc U_{n+1})}(x)$. 
        \begin{itemize}
          \item If $N\leq n$, then $x$ is covered in round $n+1$.
          \item If $N>n$ and $N=f_{A(\mc U_{p+1})}(x)$ for all $p\geq n$, then $x$ is covered in round $N$.
          \item If $N>n$ and $N\not=f_{A(\mc U_{p+1})}(x)$ for some $p>n$, then $x$ is covered in round $p+1$.
        \end{itemize}
      \end{itemize}
  \end{proof}

  \begin{definition}
    A space $X$ is \textbf{Hurewicz} if for each sequence of open covers $\mc U_n$, there are $\mc F_n \in [\mc U_n]^{<\omega}$ such that $X=\bigcup_{m<\omega}\bigcap_{m\leq n<\omega}\cup\mc F_n$.
  \end{definition}

  % Probably no good.
  % \begin{definition}
  %   A $\gamma$-cover $\mc U$ of $X$ is a countable cover such that each $x\in X$ is contained in all but finite members of $\mc U$.

  %   A $\gamma_\infty$-cover is an infinite $\gamma$-cover. 
  % \end{definition}

  % \begin{definition}
  %   A space $X$ is \textbf{Hurewicz} if and only if for each sequence $\mc U_n$ of $\gamma_\infty$-covers, there are $\mc F_n\in[\mc U_n]^{<\omega}$ such that either $\bigcup_{n<\omega} \mc F_n$ is a $\gamma_\infty$-cover, or $\mc F_N$ is a cover for some $N$.
  % \end{definition}

  % \begin{proposition}
  %   A space $X$ is Hurewicz if and only if for each sequence $\mc U_n$ of $\gamma$-covers, there are $\mc F_n\in[\mc U_n]^{<\omega}$ such that $\bigcup_{n<\omega} \mc F_n$ is a $\gamma$-cover.
  % \end{proposition}

  % \begin{proof}
  %   Suppose $X$ is Hurewicz. For each sequence $\mc U_n$ of $\gamma$-covers, either:
  %     \begin{itemize}
  %       \item Each $\mc U_n$ is a $\gamma_\infty$-cover as well. Apply Hurewicz to find $\mc F_n$ such that either $\bigcup_{n<\omega} \mc F_n$ is a $\gamma_\infty$-cover (and thus a $\gamma$-cover) or else $\mc F_N$ is a cover for some $N$, so letting $\mc F_n'=\emptyset$ for $n\not=N$ and $\mc F_N'=\mc F_N$ yields the $\gamma$-cover $\bigcup_{n<\omega} \mc F_n'=\mc F_n$.
  %       \item Some $U_N$ is not a $\gamma_\infty$-cover as it is finite. Let $\mc F_n'=\emptyset$ for $n\not=N$ and $\mc F_N=\mc U_N$ to yield the $\gamma$-cover $\bigcup_{n<\omega} \mc F_n=\mc U_n$.
  %     \end{itemize}

  %   Suppose for each sequence $\mc U_n$ of $\gamma$-covers, there are $\mc F_n\in[\mc U_n]^{<\omega}$ such that $\bigcup_{n<\omega} \mc F_n$ is a $\gamma$-cover. Then for each sequence $\mc U_n$ of $\gamma_\infty$-covers, let $\mc F_n\in[\mc U_n]^{<\omega}$ such that $\bigcup_{n<\omega} \mc F_n$ is a $\gamma$-cover. We are now done, unless $\bigcup_{n<\omega} \mc F_n$ is finite.
  % \end{proof}

@@

  \begin{theorem}
    The following are equivalent for points-$G_\delta$ $X$:
      \begin{enumerate}[(a)]
        \item $S\win\rothgame{X}$
        \item $P\win\altrothgame{X}$
        \item $S\kmarkwin{k}\rothgame{X}$ for some $k\geq 1$
        \item $P\kmarkwin{k}\altrothgame{X}$ for some $k\geq 1$
        \item $S\markwin\rothgame{X}$
        \item $P\prewin\altrothgame{X}$
        \item $X$ is almost countable
        \item $|X|\leq\omega$
      \end{enumerate}
  \end{theorem}

@@

  \begin{corollary}
    The following are equivalent for compact points-$G_\delta$ $X$:
      \begin{enumerate}[(a)]
        \item $S\win\rothgame{X}$
        \item $P\win\altrothgame{X}$
        \item $S\kmarkwin{k}\rothgame{X}$ for some $k\geq 1$
        \item $P\kmarkwin{k}\altrothgame{X}$ for some $k\geq 1$
        \item $S\markwin\rothgame{X}$
        \item $P\prewin\altrothgame{X}$
        \item $X$ is almost countable
        \item $|X|\leq\omega$
        \item $C\not\win\rothgame{X}$
        \item $O\not\win\altrothgame{X}$
        \item $X$ is Rothberger
        \item $X$ is scattered
      \end{enumerate}
  \end{corollary}

### 2013-11-24 todo.tex
added alg top result, working on meager-nwd game
Updated filling results and todos
Updated todos
Added forcing argument
housecleaning, added proximal game results

  \begin{itemize}
    \item Menger-related properties and games results
      \begin{itemize}
        \item Is there a slick characterization of $F\kmarkwin{2}\mengame{X}$ for regular/general spaces?
        \item Is $F\uparrow_{?}\mengame{X}$ or $F\uparrow_{?}\rothgame{X}$ a hereditary property under closed subsets for any type of limited information? (The Menger property is. Is Rothberger?)
      \end{itemize}
    \item Search for a class of spaces where $K\ktactwin{2}\lfkpgame{X}$ characterizes metacompact (aka implies $K\tactwin\lfkpgame{X}$)
      \begin{itemize}
        \item Investigate the ladder space suggested by G.
        \item Try zero-dimensional.
      \end{itemize}
  \end{itemize}
\end{document}

>>>>

  \begin{itemize}
    \item Menger/Rothberger properties and games results
      \begin{itemize}
        \item Is there a slick characterization of $F\kmarkwin{2}\mengame{X}$ for regular/general spaces?
        \item Is $F\uparrow_{?}\mengame{X}$ or $F\uparrow_{?}\rothgame{X}$ a hereditary property under closed subsets for any type of limited information? (The Menger property is; is Rothberger?)
        \item Investigate Markov strategies for $S$ in $\rothgame{X}$ or $P$ in $\altrothgame{X}$.
        \item $S\kmarkwin{2}\rothgame{X}\Leftrightarrow S\kmarkwin{k}\rothgame{X}$?
        \item $S\kmarkwin{2}\rothgame{\oneptcomp{\omega_1}}$ or $S\kmarkwin{2}\rothgame{\oneptlind{\omega_1}}$?
        \item $F\kmarkwin{k}\kfillgame{\kappa} \Rightarrow F\kmarkwin{k}\mengame{\oneptlind{\kappa}}$?
        \item Would Lindelof scattered spaces have a $2$-Markov strategy in the Menger game?
      \end{itemize}
    \item Filling games
      \begin{itemize}
        \item Show/disprove $F\ktactwin{3}\sfillgame{J}$ implies $F\kmarkwin{3}\fillgame{J}$.
        \item Show/disprove $F\kmarkwin{2}\mengame{\oneptlind{\kappa}}$ implies $F\kmarkwin{2}\kfillgame{\kappa}$.
      \end{itemize}
    \item Search for a class of spaces where $K\ktactwin{2}\lfkpgame{X}$ characterizes metacompact (aka implies $K\tactwin\lfkpgame{X}$)
      \begin{itemize}
        \item Investigate the ladder space suggested by G.
        \item Try zero-dimensional.
      \end{itemize}
    \item Proximity Game
      \begin{itemize}
        \item Read paper by Bell
        \item Investigate k-tacts and k-Mark for one-point compactifications
      \end{itemize}
  \end{itemize}
\end{document}
